---
title: "Final Project"
author: "Grace Aldridge"
date: "12/8/2021"
output: html_document
---

This data set was imported from [Kaggle](https://www.kaggle.com/kewagbln/absenteeism-at-work-uci-ml-repositiory). I chose to observe "Absenteeism at Work" to see what correlations I could find.

I decided that I wanted to see how the month of absence and the amount of targets hit compared to each other. I found that there are a couple of outliers in the months we observe as Summer. In the winter, there was less absenteeism and a higher percentage of targets hit.

```{r}
library(curl)

load(curl("https://raw.githubusercontent.com/Professor-Hunt/ACC8143/main/data/tips.rda"))


set.seed(0)
library(rsample)
library(tidyverse)

#perform bootstrapping with 2000 replications
Absenteeism1 <- bootstraps(as.data.frame(data.for.project$Month.of.absence), times = 100)

#view results of boostrapping
knitr::kable(head(summary(Absenteeism1),5))
```

```{r}
#info for a specific sample
Absenteeism1$splits[[1]]
```

```{r}
#mean
mean(Absenteeism1$splits[[1]]$data$`data.for.project$Month.of.absence`)
```

```{r}
#standard deviation
sd(Absenteeism1$splits[[1]]$data$`data.for.project$Month.of.absence`)
```

```{r}
#get all of them 
mean_values<-purrr::map_dbl(Absenteeism1$splits,
        function(x) {
          dat <- as.data.frame(x)$`data.for.project$Month.of.absence`
          mean(dat)
        })

#view the whole dataset
knitr::kable(mean_values)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "50%",height="300px")
```

```{r}
#estimate of the population mean
mean(mean_values)
```

```{r}
#get all of them
sd_values<-purrr::map_dbl(Absenteeism1$splits,
        function(x) {
          dat <- as.data.frame(x)$`data.for.project$Month.of.absence`
          sd(dat)
        })

#view the whole dataset
knitr::kable(sd_values)%>%
  kableExtra::kable_styling("striped")%>%
  kableExtra::scroll_box(width = "50%",height="300px")
```

```{r}
#estimate of the population standard deviation
sd(sd_values)
```

```{r}
set.seed(1)
#lets split the data 60/40
library(caret)
trainData <- createDataPartition(data.for.project$Hit.target, p = .6, list = FALSE, times = 1)

#grab the data
DataTrain <- data.for.project[ trainIndex,]
DataTest  <- data.for.project[-trainIndex,]

ggplot(data=DataTrain)+geom_point(mapping = aes(x=Month.of.absence,y=Hit.target,color=Month.of.absence),alpha=0.5) + labs(color = "Testing Targets")+ geom_point(data=DataTest, ,mapping = aes(x=Month.of.absence,y=Hit.target,)) + labs(shape = "Testing Targets") +
  ggtitle("Absenteeism")+
  theme(plot.title = element_text(hjust=0.5, size=10, face='bold'))

```
