---
title: "Machine Learning"
author: "Grace Aldridge"
date: "12/4/2021"
output: html_document
---

```{r, echo=FALSE}
library(ggplot2)
library(caret)
library(tidyverse)
```

k-Nearest Neighbors is an algorithm used to predict what the surrounding values will be in a data set based off of a sample. For example, picture a room with six people in it. Four of those people are females and one person is male. k-Nearest Neighbors would be used to predict that the sixth person is a female based off of the female to male ratio in the room.

Below, the model is being used to predict the taxonomy of an iris plant using k-nearest neighbors and classification. The chart shows the accuracy of the model, which ends up being 0.9333. There was less error when the model predicted setosa over versicolor and virginica.

This algorithm can be used in the field of accounting by predicting fraudulent firms within an industry. If there are more firms committing fraudulent activity within a certain industry over another, then auditors would be inclined to shit their focus towards that industry.

```{r}
indxTrain <- createDataPartition(y = iris[, names(iris) == "Species"], p = 0.7, list = F)

train <- iris[indxTrain,]
train1<-train%>%
  filter(Species=="setosa")%>% 
  sample_n(10)
train2<-train%>%
  filter(Species=="versicolor")%>% 
  sample_n(10)
train3<-train%>%
  filter(Species=="virginica")%>% 
  sample_n(10)
graph_train<-rbind(train1,train2,train3)

test <- iris[-indxTrain,]
graph_test<-test%>%
  sample_n(1)

knnModel <- train(Species ~., #equation or formula
                  data = graph_train, #input data to train on
                  method = 'knn', #algorithm
                  preProcess = c("center","scale"), #standardizes the data
                  tuneGrid=data.frame(k=5)) 

predictedclass<-predict(knnModel,graph_test)

predictedclass


set.seed(1)

indxTrain <- createDataPartition(y = iris[, names(iris) == "Species"], p = 0.7, list = F)

train <- iris[indxTrain,]
test <- iris[-indxTrain,]

# Fit the model on the training set
#set.seed(123)
knn_model_2 <- train(
  Species ~., 
  data = train, 
  method = "knn",
  trControl = trainControl("cv", number = 10),
  preProcess = c("center","scale"),
  tuneLength = 10
)
knn_model_2

```

```{r}
plot(knn_model_2)
```
